\begin{thebibliography}{59}
\providecommand{\url}[1]{\texttt{#1}}
\providecommand{\urlprefix}{ }

\bibitem[Allard et~al.(2012)Allard, Dushek, Coombs, and Van
  Der~Merwe]{Allard:2012gy}
Allard, J.~F., O.~Dushek, D.~Coombs, and P.~A. Van Der~Merwe, 2012.
\newblock {Mechanical Modulation of Receptor-Ligand Interactions at Cell-Cell
  Interfaces}.
\newblock \emph{Biophys J} 102:1265--1273.

\bibitem[Zhu(2013)]{Zhu:2013kq}
Zhu, C., 2013.
\newblock {Mechanochemitry: A Molecular Biomechanics View of Mechanosensing}.
\newblock \emph{Annals Biomed Eng} 42:388--404.

\bibitem[Allard and Mogilner(2012)]{Allard:2012if}
Allard, J., and A.~Mogilner, 2012.
\newblock {Traveling waves in actin dynamics and cell motility}.
\newblock \emph{Curr Op Cell Biol} 25:1--9.

\bibitem[Rangamani et~al.(2013)Rangamani, Benjamini, Agrawal, Smit, Steigmann,
  and Oster]{Rangamani:2013ce}
Rangamani, P., A.~Benjamini, A.~Agrawal, B.~Smit, D.~J. Steigmann, and
  G.~Oster, 2013.
\newblock {Small scale membrane mechanics}.
\newblock \emph{Biomech Modeling Mechanobiology} .

\bibitem[Liu et~al.(2010)Liu, Sun, Oster, and Drubin]{Liu:2010hla}
Liu, J., Y.~Sun, G.~F. Oster, and D.~G. Drubin, 2010.
\newblock {Mechanochemical crosstalk during endocytic vesicle formation}.
\newblock \emph{Curr Op Cell Biol} 22:36--43.

\bibitem[Tinevez et~al.(2009)Tinevez, Schulze, Salbreux, Roensch, Joanny, and
  Paluch]{Tinevez:2009bh}
Tinevez, J.-Y., U.~Schulze, G.~Salbreux, J.~Roensch, J.-F. Joanny, and
  E.~Paluch, 2009.
\newblock {Role of cortical tension in bleb growth}.
\newblock \emph{Proc Natl Acad Sci USA} 106:18581--18586.

\bibitem[Peleg et~al.(2011)Peleg, Disanza, Scita, and Gov]{Peleg:2011fz}
Peleg, B., A.~Disanza, G.~Scita, and N.~Gov, 2011.
\newblock {Propagating Cell-Membrane Waves Driven by Curved Activators of Actin
  Polymerization}.
\newblock \emph{PLoS ONE} 6:e18635.

\bibitem[Clark et~al.(2013)Clark, Dierkes, and Paluch]{Clark:2013ef}
Clark, A.~G., K.~Dierkes, and E.~K. Paluch, 2013.
\newblock {Monitoring Actin Cortex Thickness in Live Cells}.
\newblock \emph{Biophys J} 105:570--580.

\bibitem[Salbreux et~al.(2009)Salbreux, Prost, and Joanny]{Salbreux:2009fp}
Salbreux, G., J.~Prost, and J.~F. Joanny, 2009.
\newblock {Hydrodynamics of Cellular Cortical Flows and the Formation of
  Contractile Rings}.
\newblock \emph{Phys Rev Lett} 103:058102.

\bibitem[Hannezo et~al.(2015)Hannezo, Dong, Recho, Joanny, and
  Hayashi]{Hannezo:2015ba}
Hannezo, E., B.~Dong, P.~Recho, J.-F. Joanny, and S.~Hayashi, 2015.
\newblock {Cortical instability drives periodic supracellular actin pattern
  formation in epithelial tubes}.
\newblock \emph{Proc Natl Acad Sci USA} 112:8620--8625.

\bibitem[Fritzsche et~al.(2014)Fritzsche, Thorogate, and
  Charras]{Fritzsche:2014jw}
Fritzsche, M., R.~Thorogate, and G.~Charras, 2014.
\newblock {Quantitative Analysis of Ezrin Turnover Dynamics in the Actin
  Cortex}.
\newblock \emph{Biophys J} 106:343--353.

\bibitem[Strychalski and Guy(2013)]{Strychalski:2013eo}
Strychalski, W., and R.~D. Guy, 2013.
\newblock {A computational model of bleb formation}.
\newblock \emph{Math Med Biol} 30:115--130.

\bibitem[Charras et~al.(2009)Charras, Mitchison, and Mahadevan]{Charras:2009dp}
Charras, G.~T., T.~J. Mitchison, and L.~Mahadevan, 2009.
\newblock {Animal cell hydraulics.}
\newblock \emph{J Cell Sci} 122:3233--3241.

\bibitem[Clark et~al.(2014)Clark, Wartlick, Salbreux, and Paluch]{Clark:2014fj}
Clark, A.~G., O.~Wartlick, G.~Salbreux, and E.~K. Paluch, 2014.
\newblock {Stresses at the Cell Surface during Animal Cell Review
  Morphogenesis}.
\newblock \emph{Curr Biol} 24:R484--R494.

\bibitem[Fogelson and Mogilner(2014)]{BenFogelson:2014gx}
Fogelson, B., and A.~Mogilner, 2014.
\newblock {Computational Estimates of Membrane Flow and Tension Gradient in
  Motile Cells}.
\newblock \emph{PLoS ONE} 9:e84524.

\bibitem[Yip(2015)]{Yip:2015cb}
Yip, A.Km  Chiam, K.-H. and P.~Matsudaira, 2015.
\newblock {Traction stress analysis and modeling reveal that amoeboid migration in confined spaces is accompanied by expansive forces and requires the structural integrity of the membrane-cortex interactions}.
\newblock \emph{Integrative Biology} 7:1196--1211.

\bibitem[Weiner et~al.(2007)Weiner, Marganski, Wu, Altschuler, and
  Kirschner]{Weiner:2007gd}
Weiner, O.~D., W.~A. Marganski, L.~F. Wu, S.~J. Altschuler, and M.~W.
  Kirschner, 2007.
\newblock {An Actin-Based Wave Generator Organizes Cell Motility}.
\newblock \emph{PLoS Biology} 5:e221.

\bibitem[Leijnse et~al.(2015)Leijnse, Oddershede, and Bendix]{Leijnse:2015fd}
Leijnse, N., L.~B. Oddershede, and P.~M. Bendix, 2015.
\newblock {An updated look at actin dynamics in filopodia.}
\newblock \emph{Cytoskeleton} 72:71--79.

\bibitem[Wollman and Meyer(2012)]{Wollman:2012kha}
Wollman, R., and T.~Meyer, 2012.
\newblock {Coordinated oscillations in cortical actin and Ca2+ correlate with
  cycles of vesicle secretion}.
\newblock \emph{Nat Cell Biol} 14:1261--1269.

\bibitem[Charras(2008)]{Charras:2008ic}
Charras, G.~T., 2008.
\newblock {A short history of blebbing.}
\newblock \emph{J Microscopy} 231:466--478.

\bibitem[Charras(2008)]{Charras:2008bz}
Charras, G.~T., Coughlin, M., Mitchison, T. and Mahadevan, L., 2008.
\newblock {Life and times of a cellular bleb.}
\newblock \emph{Biophys J} 94:1836--1853.

\bibitem[Paluch and Raz(2013)]{Paluch:2013ea}
Paluch, E.~K., and E.~Raz, 2013.
\newblock {The role and regulation of blebs in cell migration}.
\newblock \emph{Curr Op Cell Biol} 25:582--590.

\bibitem[Danuser et~al.(2012)Danuser, Allard, and Mogilner]{Danuser:2012dr}
Danuser, G., J.~Allard, and A.~Mogilner, 2012.
\newblock {Mathematical Modeling of Eukaryotic Cell Migration: Insights Beyond
  Experiments}.
\newblock \emph{Annu Rev Cell Dev Biol}
  18.1-18.28.

\bibitem[Fujinami and Kageyama(1975)]{Fujinami:1975vo}
Fujinami, N., and T.~Kageyama, 1975.
\newblock {Circus movement in dissociated embryonic cells of a teleost, Oryzias
  latipes.}
\newblock \emph{J Cell Sci} 19:169--182.

\bibitem[Olson(1996)]{Anonymous:4HHO02bL}
Olson, E.~C., 1996.
\newblock {Onset of electrical excitability during a period of circus plasma
  membrane movements in differentiating Xenopus neurons.}
\newblock \emph{J Neurosci} 16:5117--5129.

\bibitem[Lim et~al.(2012)Lim, Chiam, and Mahadevan]{Lim:2012fz}
Lim, F.~Y., K.-H. Chiam, and L.~Mahadevan, 2012.
\newblock {The size, shape, and dynamics of cellular blebs}.
\newblock \emph{Europhys Lett} 100:28004.

\bibitem[Logue et~al.(2015)Logue, Cartagena-Rivera, Baird, Davidson, Chadwick,
  and Waterman]{Logue:2015jj}
Logue, J.~S., A.~X. Cartagena-Rivera, M.~A. Baird, M.~W. Davidson, R.~S.
  Chadwick, and C.~M. Waterman, 2015.
\newblock {Erk regulation of actin capping and bundling by Eps8 promotes cortex
  tension and leader bleb-based migration.}
\newblock \emph{eLife} 4.

\bibitem[Charras and Paluch(2008)]{Charras:2008gf}
Charras, G., and E.~Paluch, 2008.
\newblock {Blebs lead the way: how to migrate without lamellipodia}.
\newblock \emph{Nat Rev Mol Cell Biol} 9:730--736.

\bibitem[Friedl and Wolf(2003)]{Friedl:2003if}
Friedl, P., and K.~Wolf, 2003.
\newblock {Tumour-cell invasion and migration: diversity and escape
  mechanisms}.
\newblock \emph{Nat Rev Cancer} 3:362--374.

\bibitem[Sedzinski et~al.(2011)Sedzinski, Biro, Oswald, Tinevez, Salbreux, and
  Paluch]{Sedzinski:2011ef}
Sedzinski, J., M.~Biro, A.~Oswald, J.-Y. Tinevez, G.~Salbreux, and E.~Paluch,
  2011.
\newblock {Polar actomyosin contractility destabilizes the position of the
  cytokinetic furrow}.
\newblock \emph{Nature} 476:462--466.

\bibitem[Baum and Baum(2014)]{Baum:2014ee}
Baum, D.~A., and B.~Baum, 2014.
\newblock {An inside-out origin for the eukaryotic cell.}
\newblock \emph{BMC Biology} 12:76.

\bibitem[Ryan et~al.(2012{\natexlab{a}})Ryan, Watanabe, and
  Vavylonis]{Ryan:2012ej}
Ryan, G.~L., N.~Watanabe, and D.~Vavylonis, 2012.
\newblock {A review of models of fluctuating protrusion and retraction patterns
  at the leading edge of motile cells.}
\newblock \emph{Cytoskeleton} 69:195--206.

\bibitem[Kapustina et~al.(2013)Kapustina, Elston, and
  Jacobson]{Kapustina:2013gc}
Kapustina, M., T.~C. Elston, and K.~Jacobson, 2013.
\newblock {Compression and dilation of the membrane-cortex layer generates
  rapid changes in cell shape}.
\newblock \emph{J Cell Biol} 200:95--108.

\bibitem[Strychalski et~al.(2015)Strychalski, Copos, Lewis, and
  Guy]{Strychalski:2015fu}
Strychalski, W., C.~A. Copos, O.~L. Lewis, and R.~D. Guy, 2015.
\newblock {A poroelastic immersed boundary method with applications to cell
  biology}.
\newblock \emph{J Comp Phys} 282:77--97.

\bibitem[Young and Mitran(2010)]{Young:2010dp}
Young, J., and S.~Mitran, 2010.
\newblock {A numerical model of cellular blebbing: A volume-conserving,
  fluid{\textendash}structure interaction model of the entire cell}.
\newblock \emph{J Biomech} 43:210--220.

\bibitem[Alert et~al.(2015)Alert, Casademunt, Brugu{\'e}s, and
  Sens]{Alert:2015gz}
Alert, R., J.~Casademunt, J.~Brugu{\'e}s, and P.~Sens, 2015.
\newblock {Model for Probing Membrane-Cortex Adhesion by Micropipette
  Aspiration and Fluctuation Spectroscopy}.
\newblock \emph{Biophys J} 108:1878--1886.

\bibitem[Woolley et~al.(2013)Woolley, Gaffney, Oliver, Baker, Waters, and
  Goriely]{Woolley:2013bx}
Woolley, T.~E., E.~A. Gaffney, J.~M. Oliver, R.~E. Baker, S.~L. Waters, and
  A.~Goriely, 2013.
\newblock {Cellular blebs: pressure-driven, axisymmetric, membrane
  protrusions}.
\newblock \emph{Biomech Modelling Mechanobiol} 13:463--476.

\bibitem[Woolley et~al.(2014)Woolley, Gaffney, Waters, Oliver, Baker, and
  Goriely]{Woolley:2014jm}
Woolley, T.~E., E.~A. Gaffney, S.~L. Waters, J.~M. Oliver, R.~E. Baker, and
  A.~Goriely, 2014.
\newblock {Three mechanical models for blebbing and multi-blebbing}.
\newblock \emph{IMA J Applied Math} 79:636--660.

\bibitem[Woolley et~al.(2015)Woolley, Gaffney, and Goriely]{Woolley:2015jn}
Woolley, T.~E., E.~A. Gaffney, and A.~Goriely, 2015.
\newblock {Membrane shrinkage and cortex remodelling are predicted to work in
  harmony to retract blebs}.
\newblock \emph{R Soc Open Science} 2:150184--15.

\bibitem[Bovellan et~al.(2014)Bovellan, Romeo, Biro, Boden, Chugh, Yonis,
  Vaghela, Fritzsche, Moulding, Thorogate, J{\'e}gou, Thrasher, Romet-Lemonne,
  Roux, Paluch, and Charras]{Bovellan:2014ka}
Bovellan, M., Y.~Romeo, M.~Biro, A.~Boden, P.~Chugh, A.~Yonis, M.~Vaghela,
  M.~Fritzsche, D.~Moulding, R.~Thorogate, A.~J{\'e}gou, A.~J. Thrasher,
  G.~Romet-Lemonne, P.~P. Roux, E.~K. Paluch, and G.~Charras, 2014.
\newblock {Cellular Control of Cortical Actin Nucleation}.
\newblock \emph{Curr Biol} 24:1628--1635.

\bibitem[Paszek et~al.(2015)Paszek, DuFort, Rossier, Bainer, Mouw, Godula,
  Hudak, Lakins, Wijekoon, Cassereau, Rubashkin, Magbanua, Thorn, Davidson,
  Rugo, Park, Hammer, Giannone, Bertozzi, and Weaver]{Paszek:2015it}
Paszek, M.~J., C.~C. DuFort, O.~Rossier, R.~Bainer, J.~K. Mouw, K.~Godula,
  J.~E. Hudak, J.~N. Lakins, A.~C. Wijekoon, L.~Cassereau, M.~G. Rubashkin,
  M.~J. Magbanua, K.~S. Thorn, M.~W. Davidson, H.~S. Rugo, J.~W. Park, D.~A.
  Hammer, G.~Giannone, C.~R. Bertozzi, and V.~M. Weaver, 2015.
\newblock {The cancer glycocalyx mechanically primes integrin-mediated growth
  and survival}.
\newblock \emph{Nature} 511:319--325.

\bibitem[Helfrich(1973)]{Helfrich:1973td}
Helfrich, W., 1973.
\newblock {Elastic properties of lipid bilayers: theory and possible
  experiments.}
\newblock Zeitschrift f{\"u}r Naturforschung. Teil C: Biochemie.

\bibitem[Charras et~al.(2005)Charras, Yarrow, Horton, Mahadevan, and
  Mitchison]{Charras:2005dm}
Charras, G.~T., J.~C. Yarrow, M.~A. Horton, L.~Mahadevan, and T.~J. Mitchison,
  2005.
\newblock {Non-equilibration of hydrostatic pressure in blebbing cells}.
\newblock \emph{Nature} 435:365--369.

\bibitem[Taloni et~al.(20015)Taloni ]{Taloni:2015}
Taloni, A., E.~Kardash, O.~Salman,L.~Truskinovsky,4 S.~Zapperi, and C.~La Porta, 2015.
\newblock {Volume Changes During Active Shape Fluctuations in Cells}.
\newblock \emph{Phys Rev Lett} 114:208101.

\bibitem[Peukes and Betz(2014)]{Peukes:2014fw}
Peukes, J., and T.~Betz, 2014.
\newblock {Direct Measurement of the Cortical Tension during the Growth of
  Membrane Blebs}.
\newblock \emph{Biophys J} 107:1810--1820.

\bibitem{wise07} 
Wise, S. M., Kim, J. Lowengrub, J. S., 2007 
\newblock {Solving the regularized, strongly anisotropic Cahn-Hilliard equation by an adaptive nonlinear multigrid method}.
\newblock \emph{J Comp Phys}, 226:414-416.


\bibitem[Edelstein-Keshet(1988)]{Keshet}
Edelstein-Keshet, L., 1988.
\newblock {Mathematical Models in Biology} .

\bibitem[Idema et~al.(2013)Idema, Idema, Dubuis, Dubuis, Kang, Kang, Manning,
  Manning, Nelson, Nelson, Lubensky, and Liu]{Idema:2013ig}
Idema, T., T.~Idema, J.~O. Dubuis, J.~O. Dubuis, L.~Kang, L.~Kang, M.~L.
  Manning, M.~L. Manning, P.~C. Nelson, P.~C. Nelson, T.~C. Lubensky, and A.~J.
  Liu, 2013.
\newblock {The syncytial Drosophila embryo as a mechanically excitable medium}.
\newblock \emph{PLoS ONE} .

\bibitem[Ryan et~al.(2012{\natexlab{b}})Ryan, Petroccia, Watanabe, and
  Vavylonis]{Ryan:2012bq}
Ryan, G.~L., H.~M. Petroccia, N.~Watanabe, and D.~Vavylonis, 2012.
\newblock {Excitable Actin Dynamics in Lamellipodial Protrusion and
  Retraction}.
\newblock \emph{Biophys J} 102:1493--1502.

\bibitem[Bement et~al.(2015)Bement, Leda, Moe, Kita, Larson, Golding, Pfeuti,
  Su, Miller, Goryachev, and {others}]{bement2015activator}
Bement, W.~M., M.~Leda, A.~M. Moe, A.~M. Kita, M.~E. Larson, A.~E. Golding,
  C.~Pfeuti, K.-C. Su, A.~L. Miller, A.~B. Goryachev, and {others}, 2015.
\newblock {Activator-inhibitor coupling between Rho signalling and actin
  assembly makes the cell cortex an excitable medium}.
\newblock \emph{Nat Cell Biol} .

\bibitem[Britton(1982)]{Anonymous:OS1MPwCl}
Britton, N.~F., 1982.
\newblock {Threshold phenomena and solitary traveling waves in a class of
  reaction-diffusion systems}.
\newblock \emph{SIAM J Applied Math} .

\bibitem[Mori et~al.(2008)Mori, Jilkine, and Edelstein-Keshet]{Mori:2008hj}
Mori, Y., A.~Jilkine, and L.~Edelstein-Keshet, 2008.
\newblock {Wave-pinning and cell polarity from a bistable reaction-diffusion
  system}.
\newblock \emph{Biophys J} 94:3684--3697.

{\color{blue}
\bibitem[Strychalski and Guy(2016)]{Strychalski:HizQv1Ti}
Strychalski, W., and R.~D. Guy, 2016.
\newblock {Intracellular Pressure Dynamics in Blebbing Cells}.
\newblock \emph{Biophys J}. In press.
}

\bibitem[Huang et~al.(2013)Huang, Tang, Shi, Iglesias, and
  Devreotes]{Huang:2013ge}
Huang, C.-H., M.~Tang, C.~Shi, P.~A. Iglesias, and P.~N. Devreotes, 2013.
\newblock {An excitable signal integrator couples to an idling cytoskeletal
  oscillator to drive cell migration}.
\newblock \emph{Nat Cell Biol} 15:1307--1316.

\bibitem[Xiong et~al.(2010)Xiong, Huang, Iglesias, and Devreotes]{Xiong:2010fb}
Xiong, Y., C.-H. Huang, P.~A. Iglesias, and P.~N. Devreotes, 2010.
\newblock {Cells navigate with a local-excitation, global-inhibition-biased
  excitable network}.
\newblock \emph{Proc Natl Acad Sci USA} 107:17079--17086.

\bibitem[FitzHugh(1961)]{FitzHugh:1961il}
FitzHugh, R., 1961.
\newblock {Impulses and Physiological States in Theoretical Models of Nerve
  Membrane}.
\newblock \emph{Biophys J} 1:445--466.

\bibitem[Lee et~al.(1993)Lee, Ishihara, Theriot, and Jacobson]{Lee:1993bt}
Lee, J., A.~Ishihara, J.~A. Theriot, and K.~Jacobson, 1993.
\newblock {Principles of locomotion for simple-shaped cells}.
\newblock \emph{Nature} 362:167--171.

\bibitem[Luo et~al.(1993)]{Luo:2013}
Luo, W., C.~Yu, Z.~Lieu, J.~Allard, A.~Mogilner, M.~Sheetz, A.~Bershadsky, 2013.
\newblock {Analysis of the local organization and dynamics of cellular actin networks}.
\newblock \emph{J Cell Biol} 202:1057--1073.

\bibitem[Moeendarbary et~al.(2013)]{Moeendarbary:2013bs}
Moeendarbary, E., L.~Valon, M.~Fritzsche, A.~Harris, D.~Moulding, A.~Thrasher, E.~Stride, L. Mahadevan and G.~Charras, 2013.
\newblock {The cytoplasm of living cells behaves as a poroelastic material}.
\newblock \emph{Nature Materials} 12:253--261.

\bibitem[Thon et~al.(2012)Thon, Macleod, Begonja, Zhu, Lee, Mogilner, Hartwig,
  and Italiano]{Thon:2012dh}
Thon, J.~N., H.~Macleod, A.~J. Begonja, J.~Zhu, K.-C. Lee, A.~Mogilner, J.~H.
  Hartwig, and J.~E. Italiano, 2012.
\newblock {Microtubule and cortical forces determine platelet size during
  vascular platelet production}.
\newblock \emph{Nat Comm} 3:852--9.

\bibitem[Dobrowsky et~al.(2010)Dobrowsky, Daniels, Siliciano, Sun, and
  Wirtz]{Dobrowsky:2010dr}
Dobrowsky, T.~M., B.~R. Daniels, R.~F. Siliciano, S.~X. Sun, and D.~Wirtz,
  2010.
\newblock {Organization of Cellular Receptors into a Nanoscale Junction during
  HIV-1 Adhesion}.
\newblock \emph{PLoS Comp Biol} 6:e1000855.

\bibitem[Qi et~al.(2006)Qi, Krogsgaard, Davis, and Chakraborty]{Qi:2006ez}
Qi, S., M.~Krogsgaard, M.~M. Davis, and A.~K. Chakraborty, 2006.
\newblock {Molecular flexibility can influence the stimulatory ability of
  receptor-ligand interactions at cell-cell junctions}.
\newblock \emph{Proc Natl Acad Sci USA} 103:4416--4421.

\bibitem[Murray(1989)]{Murray:ur}
Murray, J.~D., 1989.
\newblock {Mathematical Biology}.
\newblock Springer

\bibitem[Carlson and Mahadevan(2016)]{Anonymous:roDfYIJA}
Carlson, A., and L.~Mahadevan, 2016.
\newblock {Elastohydrodynamics and kinetics of protein patterning in the
  immunological synapse}.
  \newblock \emph{PLoS Comp Biol} 11:e1004481.

\bibitem[Biro et~al.(2013)Biro, Romeo, Kroschwald, Bovellan, Boden,
  Tcherkezian, Roux, Charras, and Paluch]{Biro:2013bk}
Biro, M., Y.~Romeo, S.~Kroschwald, M.~Bovellan, A.~Boden, J.~Tcherkezian, P.~P.
  Roux, G.~Charras, and E.~K. Paluch, 2013.
\newblock {Cell cortex composition and homeostasis resolved by integrating
  proteomics and quantitative imaging.}
\newblock \emph{Cytoskeleton} 70:741--754.

\end{thebibliography}
